---
title: Tyler B. Naes' Resume
author: Tyler B. Naes
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
library(purrr)
library(tidyr)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) 
```





Aside
================================================================================



Contact {#contact}
--------------------------------------------------------------------------------




- <i class="fa fa-envelope"></i> tnaes@hotmail.com
- <i class="fa fa-github"></i> github.com/tbnaes




Skills {#skills}
--------------------------------------------------------------------------------



Programming with:

- R
- SQL
- CSS
- HTML

Creativity with:

- Writing
- Pen and Ink
- Painting
- Music



--------------------------------------------------------------------------------


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/scarlett425/cv).

Last updated on `r Sys.Date()`.


Main
================================================================================


Tyler B. Naes {#title}
--------------------------------------------------------------------------------

Through my experiences, I have built a strong background in operations and analysis. I will continue
this impassioned work through the disciplined application of coding and creativity for an employer.



Positions {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('professional_experience')
```




Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```






Academic Achievements & Projects {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('academic_achievements')
```


Programming Example {#examples}
--------------------------------------------------------------------------------

  Tempe Crash Dashboard: [tbnaes.shinyapps.io/final-project-naes](https://tbnaes.shinyapps.io/final-project-naes/).




Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/scarlett425/cv).

Last updated on `r Sys.Date()`.