---
title: Tyler B. Naes' Resume
author: Tyler B. Naes
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
library(purrr)
library(tidyr)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) 
```





Aside
================================================================================



Contact {#contact}
--------------------------------------------------------------------------------



- <i class="fa fa-phone"></i> (731) 697-6442
- <i class="fa fa-envelope"></i> tbnaes@gmail.com
- <i class="fa fa-github"></i> github.com/tbnaes




Skills {#skills}
--------------------------------------------------------------------------------


Communication

Writing

Team Oriented

Servant-Leadership

Programming with:

- HTML
- CSS
- SQL
- R

<i class="fa fa-computer"></i>
R Language Example: [tbnaes.shinyapps.io/final-project-naes](https://tbnaes.shinyapps.io/final-project-naes/).




References {#references}
--------------------------------------------------------------------------------


Rachel Evans (Former Asst. Principal and Curriculum at Karns High School)

<i class="fa fa-phone"></i> (865) 851-4398

<i class="fa fa-envelope"></i> rachel.evans@knoxschools.org



Mike Adams (Former ACT Coordinator & Colleague at Humboldt High School)

<i class="fa fa-phone"></i> (731) 487-0338

<i class="fa fa-envelope"></i> mike.adams@trentonssd.org






Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/scarlett425/cv).

Last updated on `r Sys.Date()`.


Main
================================================================================


Tyler B. Naes {#title}
--------------------------------------------------------------------------------

Through working and educational experiences, I have built myself a strong, analytic background. I am at
my best in a position of service, offering insight from a life of heavy reading and writing.



Positions {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('professional_experience')
```




Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```






Academic Achievements & Projects {data-icon=medal}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('academic_achievements')
```



```{r}
##Programming Example {#examples}
##--------------------------------------------------------------------------------
  ##Tempe Crash Dashboard: 
  ##[tbnaes.shinyapps.io/final-project-naes](https://tbnaes.shinyapps.io/final-project-naes/)

## take out of chunk and remove hashtags to activate example 
```






Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/scarlett425/cv).

Last updated on `r Sys.Date()`.